---
title: filters
toc: false
---

### Page under construction

add `construction: true` to the yaml header of a page and a random (1 of 5)
"under construction" gifs is inserted on top of the page

{{< divider 2 >}}

### Backgrounds

change the background of the html body using the yaml parameter `body_bg`. Can be set globally in `_quarto.yml` or locally in a file. The default is `microfab`.
other options are shown below (dont use the file ending, ie `body_bg: space`).


```{r bg-options}
fl <- list.files("img/bg")
fl
```


```{r bg-options-show}
#| output: asis
#| echo: false
gifs <- list.files("img/bg")
for(f in gifs){
cat("![",f,"](img/bg/",f,")",sep="")
}
```

In the same way, the background of the navbar can be changed with `nav_bg`. Here the default is `stars`.

{{< divider 2 >}}

### title gif

Add a gif to the title of a page using the yaml parameter `title_gif`. Can be set globally in `_quarto.yml` or locally in a file. default is to not display a gif. 
The gif needs to be present in the `img/` folder (dont use the file ending, ie `title_gif: banana-dance`)